% File produced by Jeremy West

\documentclass[margin,line]{res}                          % Custom class: "res.cls" file needed (included)

% Document:
\usepackage{setspace}                                     % Allows for custom margins, etc.
\usepackage{fullpage}                                     % Use the full page
% Customize document size:
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight}
\addtolength{\topmargin}{-.3in}
\addtolength{\textheight}{0.6in} 
%\usepackage{bibentry}
%\nobibliography*
\usepackage{natbib, bibentry}

%\setcitestyle{authoryear,open={((},close={))}}

\bibliographystyle{apalike}



% Font/text:
\usepackage[latin9]{inputenc}                             % Font definition and input type
\usepackage [autostyle, english = american]{csquotes}
\usepackage[T1]{fontenc}                                  % Font output type 
\usepackage{lmodern}                                      % Latin Modern fonts
\usepackage{textcomp}                                     % Supports many additional symbols
\usepackage{color}                                        % Enables colored text
\definecolor{darkblue}{rgb}{0.0,0.0,0.66}                 % Custom color: dark blue
\usepackage[hyperfootnotes=false,bookmarksopen]{hyperref} % Enable hyperlinks, expand menu subtree
\hypersetup{                                              % Custom hyperlink settings
    pdffitwindow=false,                                   % Window fit to page when opened
    pdfstartview={XYZ null null 1.00},                    % Fits the zoom of the page to 100%
    pdfnewwindow=true,                                    % Links in new window
    colorlinks=true,                                      % false: boxed links; true: colored links
    linkcolor=darkblue,                                   % Color of internal links
    citecolor=darkblue,                                   % Color of links to bibliography
    urlcolor=darkblue,                                    % Color of external links
    pdfauthor = {Your name},                              % PDF metadata - set within hypersetup
    pdfkeywords = {Institution, economics, etc.},         % PDF metadata - set within hypersetup
    pdftitle = {Your name: Curriculum Vitae},             % PDF metadata - set within hypersetup
    pdfsubject = {Curriculum Vitae},                      % PDF metadata - set within hypersetup
    pdfpagemode = UseNone}                                % PDF metadata - set within hypersetup

% Miscellaneous:
\usepackage{datetime}                                     % Custom date format for date field
\newdateformat{mydate}{\monthname[\THEMONTH] \THEYEAR}    % Defining month year date format

% Customize page headers:
\usepackage{fancyhdr}                                     % Used for custom page headers
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.5pt} 
\rhead{\footnotesize Matthew W Clance: Curriculum Vitae (\mydate \today), Page \thepage} %header at the right
\headsep = 0.5cm
% FIRST PAGE ONLY (redefine the plain pagestyle
\fancypagestyle{plain}{
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} 
\headsep = 0.0cm
\rhead{\footnotesize Curriculum Vitae updated \mydate \today}
}

% Define list environments:
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0.4em}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{.2em}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{.1em} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Place Bib in Publications

\begin{document}

\nobibliography{citations}

\name{ {\LARGE Matthew W Clance} \vspace*{.1in}}

\begin{resume}
\thispagestyle{plain} % to use first page footer

\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{0.20in}p{2.75in}p{2.75in}}
 & Department of Economics            & \textbf{Phone: }012 420 6911 \\            
 & University of Pretoria   & \textbf{Email: }\href{mailto: matthew.clance@up.ac.za}{matthew.clance@up.ac.za} \\         
 & Tukkiewerf 209 & Citizenship: USA  \\       
 & Hatfield/GP/0028  & Permanent Resident: South Africa \\
 &                   & Personal Website: \href{https://sites.google.com/view/matthew-clance/home}{Link}
 \end{tabular}
 \vspace*{.2in}


% You may of course add to or remove from this list of sections as needed

\section{\sc Degrees}
\begin{list1}
\item[] Ph.D. in Economics, Clemson University \hfill 2012 \newline  \vspace*{-.15in}
	\begin{list2}
		\item[--] Dissertation: "Essays in International Trade"
		\item[--] Job Market Paper: "Trade Costs and Margins of Trade"
		\item[--] Advisor: Professor Scott L. Baier
	\end{list2}
\item[] M.A. in Economics, Clemson University \hfill 2009 
\item[] B.S. in Economics, Georgia College \& State University \hfill 2004
\end{list1}

\section{\sc Research Interest}
\begin{list1}
\item[] International Trade, Development Economics, Applied Econometrics, Open Economy Macroeconomics
\end{list1}

\section{\sc Research Visibility}
\begin{list1}
	\item[] RePEc: \url{https://ideas.repec.org/e/pcl147.html}
	\item[] Google Scholar: \url{https://bit.ly/3hm23Oq}
	\item[] ORCID: \url{https://orcid.org/0000-0002-9280-7324}
	\item[] Publons: \url{https://publons.com/researcher/R-1518-2018/}
\end{list1}

\section{\sc Academic Experience}
\begin{list1}
\item[] Associate Professor, University of Pretoria \hfill 2022 - Present
\item[] Fellow, Pan-African Scientific Council \hfill 2021 - Present
\item[] Senior Lecturer (Assistant Professor), University of Pretoria  \hfill 2013 - 2021 \newline  \vspace*{-.15in}
	\begin{list2}
		\item[--] Courses Taught: Econometrics (H\&M), Microeconomics (H), Microeconomics (Actuarial Program), International Trade (H\&M), ERSA Workshop in Cross Sectional Econometrics (2014-2018,2020,2021)
	\end{list2}
\item[]  Graduate Instructor of Record, Clemson University \hfill 2010 - 2012 \newline  \vspace*{-.15in}
	\begin{list2}
		\item[--] Courses Taught: Principles of Microeconomics and Intermediate Macroeconomics
	\end{list2}
\item[] Teaching Assistant, Clemson University \hfill 2009 - 2012 \newline  \vspace*{-.15in}
	\begin{list2}
		\item[--] Courses Assisted: Principles of Microeconomics, Principles of Macroeconomics, and Graduate Macroeconomics 
	\end{list2}
\end{list1}

\section{\sc Research Experience}
\begin{list1}
\item[] Research Associate Consultant, Federal Reserve Bank of Atlanta \hfill 2011 - 2012
\item[] Research Assistant, Clemson University \hfill 2007 - 2011 
\end{list1}

\section{\sc Publications}
\begin{list1}
\item[] \bibentry{chisadza2022uncertainty}
\item[] \bibentry{VANDERMERWE2022102281}
\item[] \bibentry{Breitenbach:et:al:2022} 
\item[] \bibentry{Bosch:et:al:2022} 
\item[] \bibentry{BERISHA2021112603} 
\item[] \bibentry{Chisadza:Clance:2021}
\item[] \bibentry{Clance:et:al:2021}
\item[] \bibentry{Chisadza:et:al:2021}
\item[] \bibentry{su13063042}
\item[] \bibentry{chang2021reconsideration}
\item[] Clance, Matthew, Riza Demirer, Rangan Gupta, Clement Kweku Kyei, (2020) "Predicting firm-level volatility in the United States: the role of monetary policy uncertainty." \textit{Economics and Business Letters}, Universidad de Oviedo, vol.9, issue 3, pages 167-177 \url{https://doi.org/10.17811/ebl.9.3.2020.167-177}
\item[] Clance, Matthew W., Rangan Gupta, Mark E. Wohar, (2019). "Geopolitical Risks and Recessions in a Panel of Advanced: Evidence from Over a Century of Data." \textit{Applied Economics Letters}, Vol. 26, pages 1317-1321, \url{https://doi.org/10.1080/13504851.2018.1558332}
\item[] Aye, Goodness, Matthew Clance, Rangan Gupta, (2019). "The Effect of Economic Uncertainty on the Housing Market Cycle." \textit{Journal of Real Estate Portfolio Management}, Vol. 25, Issue, \url{https://doi.org/10.1080/10835547.2019.12090024}
\item[] Aye, Goodness, Matthew Clance, Rangan Gupta, (2019) "The Effectiveness of Monetary and Fiscal Policy Shocks on U.S. Inequality: The Role of Uncertainty." \textit{Quality \& Quantity: International Journal of Methodology}, 52 \url{https://doi.org/10.1007/s11135-018-0752-3}
\item[] Baier, Scott, Jeffrey Bergstrand, Matthew Clance, (2018) "Heterogeneous Effects of Economic Integration Agreements." \textit{Journal of Development Economics}, Elsevier, vol. 135(C), pages 587-608  \url{https://doi.org/10.1016/j.jdeveco.2018.08.014}
\end{list1}

\section{\sc Book Chapters}
\begin{list1}
\item[] \bibentry{VernerClance2022}
\item[] Baier, Scott L., Jeffrey Bergstrand, and Matthew Clance, "Preliminary Examination of Heterogeneous Effects on International Trade of Economic Integration Aggreements." Chapter 4 in Trade Cooperation: The Purpose, Design and Effect of Preferential Trade Aggrements. Cambridge \url{https://doi.org/10.1017/CBO9781316018453.018}
\item[] Baier, Scott L., Matthew Clance, and Gerald Dwyer, "Banking Crises and Economic Freedom." Chapter 4 in James Gwartney, Robert Lawson, and Joshua Hall, \textit{Economic Freedom of the World 2012 Annual Report} (Vancouver: The Fraser Institute), 2012, pp. 201-217 \url{http://dx.doi.org/10.2139/ssrn.2117883}
\end{list1}

\section{\sc Technical Reports}
\begin{list1}
\item[] Climate Change and Child Health: A Nigerian Perspective (2021). Prepared under Climate Research for Development, African Academy of Sciences
\end{list1}

\section{\sc Working Paper Series}
\begin{list1}
\item[] Merwe, E., Clance, M., and Yitbarek, E. (2022). "Climate Change and Child Health: A Nigerian Perspective." Working Papers 871, Economic Research Southern Africa. 
\item[] Walters, L., Chisadza, C., and Clance, M.. (2021). "Slave Trades, Kinship Structures and Women Political Participation in Africa." African Economic History Network Working Paper \#65.
\item[] Breitenbach, M. C., Chisadza, C., and Clance, M. (2021). "The Economic Complexity Index (ECI) and output volatility: High vs low income countries." Working Papers 202125, University of Pretoria, Department of Economics.
\item[] Merwe, E. , Chisadza, C., and Clance, M.. (2021). "Government Religious Preference and Intrastate Conflict." Working Papers 202124, University of Pretoria, Department of Economics.
\item[] Walters, L., Chisadza, C., and Clance, M.. (2020). "The Effect of Colonial and Pre-Colonial Institutions on Contemporary Education in Africa." Working Papers 850, Economic Research Southern Africa.
\item[] Zawaira, T., Clance, M., and Chisadza, C. (2020). "Social Institutions and Gender-Biased Outcomes in sub-Saharan Africa." Working Papers 2020101, University of Pretoria, Department of Economics.
\item[] Chipanda, B., Clance, M., and Koch, S. F. (2020). "Technological Trade Composition and Performance in African Countries." Working Papers 202057, University of Pretoria, Department of Economics.
\item[] Manoel Bittencourt, Matthew Clance and Yoseph Y. Getachew, 2020. "Trade Openness and Fertility Rates in Africa: Panel Data Evidence," Working Papers 807, Economic Research Southern Africa.
\item[] Chisadza, C., Clance, M., Gupta, R., and Wohar, M. E. (2019). "Giant Oil Discoveries and Conflicts." Working Papers 201964, University of Pretoria, Department of Economics.
\item[] Clance, M., Ma, W., and Naraidoo, R. (2019). "International Consumption Risk Sharing and Trade Transaction Costs." Working Papers 201932, University of Pretoria, Department of Economics.
\item[] Aye, G.C., Clance, M. and Gupta, R., 2018. "The Effectiveness of Monetary and Fiscal Policy Shocks on U.S. Inequality: The Role of Uncertainty," 2018 Conference, July 28-August 2, 2018, Vancouver, British Columbia 277037, International Association of Agricultural Economists.
\item[] Zawaira, T., Bittencourt, M., and Clance, M. W. (2018). "Gender Inequality and Marketisation Hypothesis in Sub-Saharan Africa." Working Papers 201876, University of Pretoria, Department of Economics
\item[] Chisadza, C. and Clance, M. (2018). "Conflict and Regional Heterogeneity." Working Papers 201852, University of Pretoria, Department of Economics.
\item[] Scott L Baier, Jeffrey H Bergstrand and Matthew W Clance, 2017. "Heterogeneous economic integration agreements' effects, gravity, and welfare." Discussion Papers 2017-05, University of Nottingham, GEP.
\item[] Walters, L., Bohlmann, H. R., and Clance, M. W. (2016). "The impact of the COMESA-EAC-SADC tripartite free trade agreement on the South African economy." Economic Research Southern Africa (ERSA) Working Paper, 635.
\item[] Bonginkosi Mamba, Andre C Jordaan and Matthew Clance, 2015. "Globalisation and Conflicts: A Theoretical Approach." Working Papers 532, Economic Research Southern Africa.
\item[] Scott L. Baier, Jeffrey H. Bergstrand and Matthew W. Clance, 2015. "Heterogeneous Economic Integration Agreement Effects," CESifo Working Paper Series 5488, CESifo.

\end{list1}

%\section{\sc Working Papers}
%\begin{list1}
%\item[] "Social Institutions and Gender-Biased Outcomes in sub-Saharan Africa." with Tendia Zawaira and Carolyn Chisadza \textit{under review}
%\item[] "Conflict and Regional Heterogeneity", with Carol Chisadza \textit{Revise and Resubmit} \newline  \vspace*{-.15in}
%\item[] "The Relationship between Economic Uncertainty and Corporate Tax Rates." with Rangan Gupta and Chi Lau \textit{under review}
%\item[] "International Consumption Risk Sharing and Transaction Costs" with Naraidoo and Ma \textit{under review}
%\item[] "Trade Openness and Fertility Rates in Africa: Panel-Data Evidence", with Bittencourt and Getachew \newline  \vspace*{-.15in}
%\item[] "Margins of Trade." with Jeffrey Bergstrand and Scott Baier \newline  \vspace*{-.15in}
%\item[] "Helpman, Melitz Rubinstein: General Equilibrium Analysis." with Scott Baier and Matt Cole \newline  \vspace*{-.15in}
%\item[] "Conditional Density Estimation: Application to International Trade." \newline  \vspace*{-.15in}
%\end{list1}

\section{\sc Presentations}
\begin{list1}
\item[] ESSA Biennial Conference (2019)
\item[] Africa Meeting of the Econometrics Society (Algeria-2017)
\item[] ESSA Biennial Conference (2017)
\item[] Africa Meeting of the Econometrics Society (South Africa-2016)
\item[] Politics, Finance and Growth Workshop (SARB-2016)
\item[] ESSA Biennial Conference (2015)
\item[] ERSA International Trade Workshop (2014)
\item[] University of Pretoria Economics Seminar (2014)
\item[] Graduate Student Seminar, Clemson University (2008, 2009)
\item[] Job Market Candidate Workshop, Clemson University (2011)
\item[] Macroeconomics Workshop, Clemson University (2011)
\end{list1}

\section{\sc Postgraduate Supervision}
\begin{list1}
\item[] \textbf{PhD: }Blessing Chipanda (expected completion 2022), Leone Walters (2022, Co-supervisor) Tendai Zawaira (2021), Adel Bosch (2020, Co-supervisor)
\item[] \textbf{Masters: } Ndabenhle Manyoni (2022), Dimakatso Mkwanazi (2022), Eduard van der Merwe (2021), Courtney Paulse (2020), John Verner (2018), Keaoleboga Mncube (2018), Charl van Schoor (2018), Dylan Brewer (2018), Leone Walters (2015), Vanessa Kasongo (2015), Mapule Mofokeng (2014)
\item[] \textbf{Honours: } Sane Hlatshwayo (2021), Temoso Magabane (2021), Brandon Meyer (2021), Jonathan Le Grange (2020), Ndabenhle Manyoni (2020), Adinda Behrens (2019), Courtney Paulse (2019), Eduard van der Merwe (2019), Phemelo Kekana (2018), Daniel Brink (2018), Ashley Pan (2017), John Verner (2017), Phanuel Sibasa (2017), Charl van Schoor (2016), Keaoleboga Mncube (2016), Mbavhi Masetla (2016), Lerato Reid (2016), Tessie Chinembiri (2015), Thamsanga Nhlapo (2015), Lloyd Miller (2014), Derrick Venter (2014), Takalani Mahaseni (2013), Monde Mkhwanazi (2013)
\end{list1}

\section{\sc Honors}
\begin{list1}
\item[] Best Junior Researcher in Economic Sciences 2019 (UP)
\item[] Best First Publication 2018 (UP)
\item[] Post-Graduate Teaching 2015 (UP)
\item[] Research Development Programme 2014-2016 (UP)
\item[] Staff Exchange Bursary 2014-2016 (UP)
\item[] Graduate Assistant Bursary, Clemson University, 2007-2012
\item[] Charles G. Koch Annual Fellowship, Clemson University, 2008
\end{list1}

\section{\sc Professional Services}
\begin{list1}
\item[] \textbf{Conference: } ESSA Conference Selection Committee (2021)
\item[] \textbf{Referee: }Economic Modeling, Review of International Economics, World Development, Journal of Economic Surveys, International Review of Economics and Finance, ERSA, SAJE, Review of World Economics, Government Information Quarterly, Technology in Society 
\item[] \textbf{Department Service: }AACSB Assurance of Learning Committee (2018-), Masters Coordinator (2019-), Masters Program Committee (2015-), Graduate Admission Committee (2015-2017), Search Committee (2014) 
\item[] \textbf{External Examiner: }Economics and Economic Sciences Honours (All courses) - University of the Witwatersrand (2015-2017); Tshwane University of Technology (2018-) - Development, Econometrics, Intermediate Macroeconomics; University of Western Cape (2018-) - International Trade, Financial Trade; Masters Thesis - University of Cape Town (2018), University of Johannesburg (2020), UNISA (2021), UKZN (2021)
\end{list1}

\section{\sc References}
\vspace{.05in}
\begin{tabular}{@{} p{2in} p{2.2in} p{2in} p{2in} }
& Prof. Scott L. Baier                    & Prof. Jeffrey Bergstrand & Yoseph Getachew \\
& John E. Walker Dept. of Economics         & Dept. of Finance & Dept. of Economics\\
& Clemson University                           & University of Notre Dame & University of Pretoria \\
& (864) 656-4534                           &  (574) 631-6761 & (012) 420-3461 \\
& \href{mailto:sbaier@clemson.edu}{sbaier@clemson.edu} & \href{mailto:jbergstr@nd.edu}{jbergstr@nd.edu} & \href{mailto:yoseph.getachew@up.ac.za}{yoseph.getachew@up.ac.za} \\
&                                      & \\
%& Prof. Three                         & Prof. Four (etc.) \\
\end{tabular}

\end{resume}

%\bibliographystyle{plainnat}
%\bibliography{citations}
\end{document}