---
title: "Setup Guide"
output:
  html_document:
    toc: true
    toc_float: true
---

# Preparation for R and RStudio Installation

- Visit the [CRAN website](http://lib.stat.cmu.edu/R/CRAN/) and download the version for your operating system.

- There are three options, but the instructions below focus on **Windows**:
  - Download R for Linux (Debian, Fedora/Redhat, Ubuntu)
  - Download R for macOS
  - Download R for Windows

- Visit the [Posit website](https://posit.co/downloads/) to download RStudio for your platform.

- **Note:** R can function without RStudio, but RStudio requires R to run.

- If you use a Mac, refer to the following guide for installing R and RStudio:
  - [TC Technology Knowledge Base](https://teacherscollege.screenstepslive.com/a/1135059-install-r-and-rstudio-for-mac)

## Checking If R and RStudio Are Installed

Open RStudio and check the "Console" (typically in the bottom-left panel unless you have changed the layout) to see the current version of R installed.

- To update to the latest version:
  - Go to the **Help** tab $\rightarrow$ **Check for Updates**

## Installing R and RStudio on Windows

- Run the downloaded R installer and use the default options.
  - Both 32-bit and 64-bit versions are installed, but most computers will use the 64-bit version.

- Run the downloaded RStudio installer (a `.exe` file).



# RMarkdown

RMarkdown allows you to create documents (PDF, HTML, Word, or slides) that integrate code and text. It is useful for reproducible research and teaching with dynamic content.

- Open RStudio and install the required packages:
```{r, echo=TRUE, eval=FALSE}
install.packages("rmarkdown")
install.packages("tinytex") # TinyTeX (a lightweight LaTeX distribution)
tinytex::install_tinytex()
```

# Introduction to RMarkdown

This section provides a basic example of an RMarkdown file. You can write text, include R code, and generate output dynamically.

## Load Required Packages
```{r setup, echo=TRUE}
library(ggplot2) # Load ggplot2 for visualization
```

## Basic Calculations in R
```{r, echo=TRUE}
# Simple arithmetic
x <- 5 + 3
x # Output result
```

## Create a Simple Plot
```{r, echo=TRUE}
# Generate random data
data <- data.frame(x = rnorm(100), y = rnorm(100))

# Scatter plot using ggplot2
ggplot(data, aes(x = x, y = y)) +
  geom_point() +
  theme_minimal()
```

## Inline Code Example
The value of `x` computed earlier is `r x`.

## Conclusion
- You can write formatted text.
- Run and display R code within the document.
- Generate tables, plots, and dynamically update results.

Click the **Knit** button in RStudio to generate an HTML, PDF, or Word document.
